Discovering governing reactions from concentration data

### 2018-08-28 docs/manuscript.tex
lsq rates
wip

	For $\alpha=0$ the minimization problem reduces to constrained least-squares. In order to solve (\ref{method:minimizationproblem}) the numerical sequential least-squares minimizer SLSQP \cite{Kraft1988} is applied via the software package SciPy \cite{SciPy}. Since only the concentration data $\mathbf{X}$ is available but not its temporal derivative $\dot{\mathbf{X}}$, it is approximated numerically by second order finite differences with the exception of boundary data. Once the pair $(\mathbf{X}, \dot{\mathbf{X}})$ is obtained, the problem becomes invariant under temporal reordering. Hence, when presented with multiple trajectories the data matrices $\mathbf{X}_i$ and $\dot{\mathbf{X}}_i$ can simply be concatenated.

@@

	\begin{figure}
		\centering
		\includegraphics[width=.5\columnwidth]{./figures_tex/case2}
		\caption{Convergence of the estimation error when estimating the system described in Sec.~\ref{sec:case-1} with decreasing levels of noise by application of the minimization problem (\ref{method:minimizationproblem}). The level of noise is regulated by the number of measurements being averaged. The hyperparameters for each level of noise were estimated using 10-fold cross validation. This was repeated 10 times giving rise to the mean and standard deviation depicted by dark blue graph and shaded blue area, respectively. The failure rate is the number of incorrectly identified processes. The estimation error is given by the $L_1$ difference of the generating reaction rates $\hat{\xi}$ and the estimated reaction rates $\xi_\mathrm{CV}$.}
		\label{fig:case2-convergence}
	\end{figure}

>>>>

	For $\alpha=0$ the minimization problem reduces to constrained least-squares (LSQ). In order to solve (\ref{method:minimizationproblem}) the numerical sequential least-squares minimizer SLSQP \cite{Kraft1988} is applied via the software package SciPy \cite{SciPy}. Since only the concentration data $\mathbf{X}$ is available but not its temporal derivative $\dot{\mathbf{X}}$, it is approximated numerically by second order finite differences with the exception of boundary data. Once the pair $(\mathbf{X}, \dot{\mathbf{X}})$ is obtained, the problem becomes invariant under temporal reordering. Hence, when presented with multiple trajectories the data matrices $\mathbf{X}_i$ and $\dot{\mathbf{X}}_i$ can simply be concatenated.

@@

	\begin{figure}
		\centering
		\includegraphics[width=.7\columnwidth]{./figures_tex/case2}
		\caption{Convergence of the estimation error when estimating the system described in Sec.~\ref{sec:case-1} with decreasing levels of noise by application of the minimization problem (\ref{method:minimizationproblem}) for $\alpha=0$ (LSQ) and a $(\alpha, \lambda)$ combination found through $10$-fold cross-validation (regularized). The level of noise is regulated by the number of measurements being averaged. The procedure was repeated 10 times with different realizations giving rise to the mean and standard deviation depicted by dark blue graph and shaded blue area, respectively. The failure rate is the number of incorrectly identified processes up to the cutoff value introduced in Sec.~\ref{sec:case-1}. The estimation error is given by the $L_1$ difference of the generating reaction rates $\xi$ and the estimated reaction rates $\hat{\xi}$.}
		\label{fig:case2-convergence}
	\end{figure}
